\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-27 doc/sui14/iteration3.tex
minor changes: grammar in iteration3, line separater in relatedwork
[iteration3]: remove merge conflict

Both {\em Naive IR} and {\em Intensity IR} rely on list navigation on the near-eye display for the refinement step. The list interface has a few clear shortcomings: navigation actions map poorly to real world results, and the users must switch their focus back and forth between the physical scene and the near-eye display. These problems motivated us to design an approach that harnesses the head orientation during the {\em refinement} stage.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_principle.png}
\caption{This illustrates that when the change of user's absolution position doesn't change the relative relationship of physical targets.}
\label{fig:third_principle}
\end{figure}

>>>>

Both {\em Naive IR} and {\em Intensity IR} rely on list navigation on the
near-eye display for the refinement step. The list interface has a few clear
shortcomings: navigation actions map poorly to real world results, and
users must switch their focus back and forth between the physical scene and the
near-eye display. These problems motivated us to design an approach that
harnesses the head orientation during the {\em refinement} stage.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_principle.png}
\caption{This illustrates that the change of a user's absolution position
doesn't change the relative relationship of physical targets.}
\label{fig:third_principle}
\end{figure}
